---
title: 'Association Rules: Census Bureau'
output:
  html_document:
    df_print: paged
---

Upload the required libraries
```{r}
library('arules')
library('arulesViz')
``` 

Read the dataset in data.frame format
```{r}
data("AdultUCI")
```

Remove useless fields
```{r}
AdultUCI[["fnlwgt"]] <- NULL
AdultUCI[["education-num"]] <- NULL
AdultUCI<-AdultUCI[complete.cases(AdultUCI), ]
```

Convert numeric fields into categorical ones
```{r}
AdultUCI[["age"]] <- ordered(cut(AdultUCI[["age"]], c(15,25,45,65,100)),
labels = c("Young", "Middle-Aged", "Senior", "Old"))
AdultUCI[["hours-per-week"]] <- ordered(cut(AdultUCI[["hours-per-week"]],c(0,25,40,60,168)),
labels = c("Part-time", "Full-time", "Over-time", "Workaholic"))

AdultUCI[["capital-gain"]] <- ordered(cut(AdultUCI[["capital-gain"]],
c(-Inf,0,median(AdultUCI[["capital-gain"]][AdultUCI[["capital-gain"]]>0]),Inf)),
labels = c("None", "Low", "High"))

AdultUCI[["capital-loss"]] <- ordered(cut(AdultUCI[["capital-loss"]],
c(-Inf,0, median(AdultUCI[["capital-loss"]][AdultUCI[["capital-loss"]]>0]),Inf)), 
labels = c("None", "Low", "High"))
```

Convert the dataset from data.frame format into transactions format
```{r}
Adult <- as(AdultUCI, "transactions")
Adult
#inspect(Adult[3])
Adult@itemInfo$labels
```

Run the Apriori Algorithm and display a subset of rules
```{r}
rules <- apriori(Adult,parameter=list(minlen=2,maxlen=5,support=0.001,confidence=0.5),control = list(verbose=F))
rules.sortedbylift <- sort(rules, by="lift")
inspect(rules.sortedbylift[1:20])
```

Remove redundant rules
```{r}
#A rule is redundant if a more general rule with the same or a higher confidence exists.
#A rule is more general if it has the same RHS but one or more items removed from the LHS.
rules <- (rules[!is.redundant(rules)])
```

Extract subsets of rules of interest (i.e. analyse rules with the consequence "income=large")
```{r}
incomeLarge <- subset(rules,(rhs %in% paste0("income=large")))
```

Inspect the best 10 rules according to the lift
```{r}
incomeLarge.sorted <- sort(incomeLarge, by="lift")
inspect(incomeLarge.sorted[1:20])
```

**********************************
SCATTER PLOT AND TWO-KEY PLOT
**********************************
```{r}
plot(incomeLarge,measure=c("support","confidence"),shading="lift",control=list(main="Scatter Plot"),jitter=0)
plot(incomeLarge,shading="order",control=list(main = "Two-Key Plot"),jitter=0)
```

**********************************
GRAPH-BASED VISUALIZATION
**********************************
```{r fig.height=9, fig.width=7}
plot(incomeLarge.sorted[1:3],method="graph")
```

**********************************
PARALLEL-COORDINATES PLOT
**********************************
```{r}
plot(incomeLarge.sorted[1:10], method="paracoord",control=list(reorder=TRUE, main = "Top 10 rules for 'Large Income'"))
```

**********************************
DOUBLE-DECKER PLOTS
**********************************
```{r}
inspect(incomeLarge.sorted[5])
plot(incomeLarge.sorted[5],method="doubledecker",data = Adult, control=list(main = "Double-Decker Plot"))
```











